Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2014-11-24 AO_bondedSi.tex
Get rid of the 373 K temp on n and F plot, closes #7

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/SiIndexAOmgsFinesseFig.pdf}}
\caption{Plot of refractive index, $n$, and coefficient of finesse, $F$, as a function of wavelength, $\lambda$.\label{figSiIndexFinesse} We computed the temperature dependent refractive index from the tabulations of \cite{2006SPIE.6273E..77F}, and extrapolated past their upper temperature bound to estimate values near 373 K.  The coefficient of finesse is defined in Equation \ref{eq:FabPerot}.  The minuscule temperature dependence is largely negligible, and for the rest of the paper we assume room temperature refractive index.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/SiIndexAOmgsFinesseFig.pdf}}
\caption{Plot of refractive index, $n$, and coefficient of finesse, $F$, as a function of wavelength, $\lambda$.\label{figSiIndexFinesse} We computed the temperature dependent refractive index from the tabulations of \cite{2006SPIE.6273E..77F}.  The coefficient of finesse is defined in Equation \ref{eq:FabPerot}.  The minuscule temperature dependence is largely negligible, and for the rest of the paper we assume room temperature refractive index.}
\end{figure}
